---
title: "RO-MAN 2020 Plots"
output:
  html_document:
    theme: readable
    code_folding: hide
    df_print: tibble
    toc: true
    toc_float: true
    toc_depth: 2
    number_sections: true
---

```{r message=FALSE, warning=FALSE}
library(car)
library(stats)
library(grid)
library(gridExtra)
library(fitdistrplus)
# library(dplyr)
# library(forcats)
# library(tibble)
# library(tidyr)
# library(readr)
# library(ggplot2)
# library(stringr)
library(tidyverse)
library(ggsignif)
library(ggthemes)
library(jtools)
library(broom)
library(modelr)
library(loo)
# library(rstanarm)
library(brms)
library(bayesplot)
library(GGally)
library(tidybayes)
library(bayestestR)
library(sjstats)
library(parameters)
library(see)

# Setup for multiprocessing
options(mc.cores = 4)
# library(future)
# plan(multiprocess)

# Make the default coding of contrasts sum-coding; just in case
options(contrasts = c("contr.sum", "contr.poly"))
```

Global options:

```{r}
# Script execution globals
train_models = F     # Retrain the MCMC models. Also infer unknown demographics
plot_posteriors = F  # Plot the posterior distributions (debug)
plot_paper_posteriors = T  # Plot the posterior distributions that are in the paper
plot_diagnostics = T # Plot the diagnostics
report_bayesfactors = F  # Report the Bayes Factor scores of model parameters
default_seed = 0x1331 # For repeatable models and diagnostics
data_folder = "~/Documents/GT/Research/Data/arbitration/2019-12-09/results"
```

Helper functions:

```{r, message=FALSE, warning=FALSE}
# Create a simple coding contrasts matrix
contr.deviation = function(nlevels) {
  x1 = contr.treatment(nlevels)
  x2 = matrix(rep(1/nlevels, (nlevels-1) * nlevels), ncol = (nlevels-1))
  return(x1-x2)
}

# NOTE: For now we're ignoring this advice
# # Use a simple coding contrasts matrix to add our own contrasts columns
# # Explained in: http://talklab.psy.gla.ac.uk/tvw/catpred/
# create_simple_contrasts = function(d, column_name) {
#  factor_column = d %>% pull(column_name)
#  contrast_matrix = contr.deviation(length(levels(factor_column)))
# }

# Save a model
saveModel = function(model, folder = data_folder) {
  saveRDS(model, file = file.path(folder, paste(substitute(model), ".rds", sep = '')))
}

# Load a model
loadModel = function(model_name, folder = data_folder) {
  return(readRDS(file.path(folder, paste(model_name, '.rds', sep = ''))))
}
```

Data loading:

```{r, message=F, warning=F}
# Load the CSV files. If the age_group fill model is run again and we get a different output,
# then remember to update the value here
loadCSV = function(filename, age_group_fill, contrast_func) {
  dat = read_csv(
    file.path(data_folder, filename),
    col_types = cols(
      study_condition = col_factor(),
      suggestion_type = col_factor(levels = c("NONE", "AX", "DX", "DXAX")),
      noise_level = col_factor(ordered = T),
      # gender = col_factor(levels = c("F", "M", "U")),
      # age_group = col_factor(levels = seq(from = 0, to = 8)),  # We don't load this as a factor yet
      robot_experience = col_factor(levels = seq(from = 0, to = 4))
    )
  )

  # Relabel the factors
  dat = dat %>%
    mutate(study_condition = fct_recode(study_condition,
                                        BASELINE="1",
                                        DX_100="2", AX_100="3", DXAX_100="4",
                                        DX_90="5", AX_90="6", DXAX_90="7",
                                        DX_80="8", AX_80="9", DXAX_80="10")) %>%
    mutate(study_condition = fct_relevel(study_condition, c("DX_100", "AX_100", "DXAX_100",
                                                            "DX_90", "AX_90", "DXAX_90",
                                                            "DX_80", "AX_80", "DXAX_80")))

  # Relevel the non-binary gender and make it a factor
  dat = dat %>%
    mutate(gender = ifelse(gender == "U", "M", gender)) %>%
    mutate(gender = factor(gender, levels = c("F", "M")))

  # Change binary responses to integers
  dat = dat %>% mutate(scenario_completed = as.integer(scenario_completed))

  # Relevel age_group and make it a factor
  dat = dat %>%
    mutate(age_group = ifelse(age_group == 0, age_group_fill, age_group)) %>%
    mutate(age_group = factor(age_group, levels = seq(from = 0, to = 8)))

  # Create an unordered noise_level. Also drop unused levels
  dat$age_group = droplevels(dat$age_group)
  dat$gender = droplevels(dat$gender)
  dat$noise_level_f = factor(dat$noise_level, ordered = F)

  # Set the contrasts for everything
  contrasts(dat$age_group) = contrast_func(length(levels(dat$age_group)))
  contrasts(dat$robot_experience) = contrast_func(length(levels(dat$robot_experience)))
  contrasts(dat$gender) = contrast_func(length(levels(dat$gender)))

  contrasts(dat$has_ax) = contrast_func(2)
  contrasts(dat$has_dx) = contrast_func(2)
  contrasts(dat$has_noise) = contrast_func(2)
  contrasts(dat$has_dxax) = contrast_func(2)
  contrasts(dat$has_ax_only) = contrast_func(2)
  contrasts(dat$has_dx_only) = contrast_func(2)
  contrasts(dat$has_suggestions) = contrast_func(2)
  contrasts(dat$suggestion_type) = contr.helmert(4)  # This is a hardcode

  contrasts(dat$noise_level_f) = contrast_func(length(levels(dat$noise_level_f)))

  # Return the data frame
  return(dat)
}

# Get the users df and the actions df
users = loadCSV("users.csv", 4, contr.sum)
actions = loadCSV("actions.csv", 4, contr.sum)

# Change more binary responses to integers
# actions %>%
#   mutate(optimal_ax)
actions = actions %>%
  mutate(optimal_ax = as.integer(optimal_ax),
         chose_ax = as.integer(chose_ax),
         optimal_dx = as.integer(optimal_dx),
         chose_dx = as.integer(chose_dx))

# Relabel user ids to be in the range 1-200. Otherwise, we're using DB ids
# The user ID column in the users table that we can now join on is X1
actions$user_id = actions %>% group_indices(user_id)

# Rescale state ids
actions$state_idx_rescaled = scales::rescale(actions$state_idx)

# Code to relevel the age group factor to remove unused levels. Also, predict the
# value of the 1 unknown age from the other indicators of demographics
# NOTE: If we retrain the model and the output doesn't match the hardcoded
# values, then update those values
if (train_models) {
  plot_df = subset(users, users$age_group != 0)
  plot_df$age_group = factor(plot_df$age_group, levels = seq(from = 0, to = 8), ordered = T)
  plot_df$age_group = droplevels(plot_df$age_group)
  age_group_model = brm(age_group ~ gender + robot_experience, data = plot_df, family = "cumulative")
  data_to_predict = users %>% filter(age_group == 0) %>% select(c("robot_experience", "gender"))
  as_tibble(predict(age_group_model, data_to_predict))
# # A tibble: 1 x 7
#   `P(Y = 2)` `P(Y = 3)` `P(Y = 4)` `P(Y = 5)` `P(Y = 6)` `P(Y = 7)` `P(Y = 8)`
#        <dbl>      <dbl>      <dbl>      <dbl>      <dbl>      <dbl>      <dbl>
# 1     0.0838      0.202      0.215      0.188      0.110      0.089      0.111
  rm(age_group_model)
}
```

Use this notebook to generate the final plots from `iros2020.Rmd`.


# Scenario Completed

Load the data and the models:

```{r}
plot_df = users %>%
  select(X1, id, study_condition, start_condition, num_optimal,
         age_group, gender, robot_experience,
         noise_level, noise_level_f, has_noise, suggestion_type,
         has_dx, has_ax, has_ax_only, has_dx_only, has_dxax,
         scenario_completed)

scenario_completed.model.t = loadModel("scenario_completed.model.t")
scenario_completed.model.v = loadModel("scenario_completed.model.v")
```

```{r, fig.width=3.5, fig.height=5}
gg_df = plot_df %>%
  mutate(scenario_completed = factor(scenario_completed)) %>%
  mutate(scenario_completed = fct_recode(scenario_completed, Unresolved="0", Resolved = "1"),
         noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0"),
         suggestion_type = fct_recode(suggestion_type, BASELINE="NONE")) %>%
  count(suggestion_type, noise_level, scenario_completed)

gg_df %>%
  ggplot(aes(suggestion_type, n / 20, fill=scenario_completed)) +
    geom_bar(stat = "identity") +
    facet_grid(rows = vars(noise_level)) +
    labs(y = "Fraction of participants that resolved fault", x = NULL) +
    scale_y_continuous(breaks = c(0, 0.5, 1.0)) +
    scale_fill_economist() +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          legend.title = element_blank(),
          legend.position = "bottom",
          axis.title.y = element_blank())
```

Significance Results:

1. Large positive effect of AX
1. Large positive effect of DXAX
1. Small U-shaped effect of accuracy

So the related plots:


```{r, fig.width=3.5, fig.height=2.5}
eff = fixef(scenario_completed.model.t)
base_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  - eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
ax_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
dx_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + (2 * eff["suggestion_type2", "Estimate"])
  - eff["suggestion_type3", "Estimate"]
)
dxax_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + (3 * eff["suggestion_type3", "Estimate"])
)

gg_df = plot_df %>%
  mutate(scenario_completed = factor(scenario_completed)) %>%
  mutate(scenario_completed = fct_recode(scenario_completed, Unresolved="0", Resolved = "1")) %>%
  count(suggestion_type, has_ax_only, has_dx_only, has_dxax, noise_level, scenario_completed) %>%
  mutate(has_ax_only = fct_recode(has_ax_only, "No AX"="FALSE", "AX"="TRUE"),
         has_dx_only = fct_recode(has_dx_only, "No DX"="FALSE", "DX"="TRUE"),
         has_dxax = fct_recode(has_dxax, "No DXAX"="FALSE", "DXAX"="TRUE"),
         noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
  mutate(estimate = ifelse(suggestion_type == "NONE", base_eff, -1)) %>%
  mutate(estimate = ifelse(suggestion_type == "AX", ax_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DX", dx_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DXAX", dxax_eff, estimate)) %>%
  mutate(suggestion_type = fct_recode(suggestion_type, BASELINE="NONE"))

gg_df %>%
  filter(scenario_completed == 'Resolved') %>%
  ggplot(aes(suggestion_type, n/20, group = suggestion_type, colour = suggestion_type)) +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    geom_signif(y_position = 1.05, xmin = 1, xmax = 2, annotation = "***", textsize = 8, color = "black") +
    geom_signif(y_position = 1.15, xmin = 1, xmax = 4, annotation = "***", textsize = 8, color = "black") +
    scale_y_continuous(limits = c(0.5, 1.2), breaks = c(0.5, 0.75, 1.0)) +
    labs(y = "Fraction of participants that resolved fault", x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

```{r, fig.width=3.5, fig.height=2.5}
eff = fixef(scenario_completed.model.v)
noise_0_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f1","Estimate"])
noise_1_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f2","Estimate"])
noise_2_eff = inv_logit_scaled(eff["Intercept", "Estimate"] - eff["noise_level_f1","Estimate"] - eff["noise_level_f2","Estimate"])

gg_df = gg_df %>%
  mutate(estimate = if_else(noise_level == "Acc: 100%", noise_0_eff, estimate)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 90%", noise_1_eff, estimate)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 80%", noise_2_eff, estimate)) %>%
  mutate(noise_level = fct_rev(noise_level))

gg_df %>%
  filter(scenario_completed == 'Resolved') %>%
  ggplot(aes(noise_level, n/20, group = noise_level, colour = noise_level)) +
    geom_hline(yintercept = inv_logit_scaled(eff["Intercept", "Estimate"]),
               size = .7, linetype = "dashed", color = "grey") +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    annotate("segment",
             x = 3, y = noise_0_eff,
             xend = 2, yend = noise_1_eff,
             colour = "black") +
    annotate("segment",
             x = 1, y = noise_2_eff,
             xend = 2, yend = noise_1_eff,
             color = "black") +
    annotate("text",
             x = 3.5,
             y = inv_logit_scaled(eff["Intercept", "Estimate"] - 0.85),
             label = "Mean of all levels",
             angle = 90,
             group = NA,
             colour = "black") +
    scale_y_continuous(limits = c(0.5, 1.1), breaks = c(0.5, 1.0)) +
    labs(y = "Fraction of participants that resolved fault", x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    scale_size_area(max_size = 1) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
    legend_none()
```


```{r, echo=F, results=F, message=F, warning=F}
rm(scenario_completed.model.t, scenario_completed.model.v)
gc()
```


# Taking the Optimal Action for a State

Load the data and the models:

```{r}
plot_df = actions %>%
  select(X1, id, user_id, study_condition, start_condition, num_optimal,
         state_idx, state_idx_rescaled,
         age_group, gender, robot_experience,
         noise_level, noise_level_f, has_noise, suggestion_type,
         has_dx, has_ax, has_ax_only, has_dx_only, has_dxax,
         scenario_completed, num_actions, optimal_ax)

optimal_ax.model.t = loadModel("optimal_ax.model.t")
optimal_ax.model.v = loadModel("optimal_ax.model.v")
```

```{r, fig.width=3.5, fig.height=5}
gg_df =
  plot_df %>%
    mutate(optimal_ax = factor(optimal_ax)) %>%
    mutate(user_id = factor(user_id)) %>%
    mutate(optimal_ax = fct_recode(optimal_ax, incorrect="0", correct = "1"),
           noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0"),
           suggestion_type = fct_recode(suggestion_type, BASELINE="NONE")) %>%
    count(user_id, suggestion_type, noise_level, optimal_ax, num_actions,
          name = "num_optimal_ax")

gg_df %>%
  filter(optimal_ax == "correct") %>%
  ggplot(aes(suggestion_type, num_optimal_ax / num_actions, fill=suggestion_type)) +
    geom_boxplot() +
    facet_grid(rows = vars(noise_level)) +
    labs(y = "Fraction of optimal actions", x = NULL) +
    scale_y_continuous(breaks = c(0, 0.5, 1.0)) +
    scale_fill_economist() +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

Significance Results:

1. Medium positive effect of AX
1. Medium positive effect of DXAX

So the related plots:

```{r, fig.width=3.5, fig.height=5}
eff = fixef(optimal_ax.model.v)
base_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  - eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
ax_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
dx_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + (2 * eff["suggestion_type2", "Estimate"])
  - eff["suggestion_type3", "Estimate"]
)
dxax_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + (3 * eff["suggestion_type3", "Estimate"])
)

gg_df = plot_df %>%
  mutate(scenario_completed = factor(scenario_completed)) %>%
  mutate(scenario_completed = fct_recode(scenario_completed, Unresolved="0", Resolved = "1"),
         has_ax_only = fct_recode(has_ax_only, "No AX"="FALSE", "AX"="TRUE"),
         has_dx_only = fct_recode(has_dx_only, "No DX"="FALSE", "DX"="TRUE"),
         has_dxax = fct_recode(has_dxax, "No DXAX"="FALSE", "DXAX"="TRUE"),
         noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
  count(user_id, suggestion_type, optimal_ax, num_actions, has_ax_only, has_dx_only, has_dxax, noise_level,
        name = "num_optimal_ax") %>%
  mutate(estimate = ifelse(suggestion_type == "NONE", base_eff, -1)) %>%
  mutate(estimate = ifelse(suggestion_type == "AX", ax_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DX", dx_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DXAX", dxax_eff, estimate)) %>%
  mutate(suggestion_type = fct_recode(suggestion_type, BASELINE="NONE"))

gg_df %>%
  filter(optimal_ax == "1") %>%
  ggplot(aes(suggestion_type, num_optimal_ax / num_actions, group = suggestion_type, colour=suggestion_type)) +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    geom_signif(y_position = 1.05, xmin = 1, xmax = 2, annotation = "**", textsize = 8, color = "black") +
    geom_signif(y_position = 1.15, xmin = 1, xmax = 4, annotation = "**", textsize = 8, color = "black") +
    scale_y_continuous(limits = c(0.0, 1.2), breaks = c(0.0, 0.5, 1.0)) +
    labs(y = NULL, x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

```{r, echo=F, results=F, message=F, warning=F}
rm(optimal_ax.model.t, optimal_ax.model.v)
gc()
```


# Choosing the Correct Diagnosis for a State

Load the data and the models:

```{r}
plot_df = actions %>%
  select(X1, id, user_id, study_condition, start_condition, num_optimal,
         state_idx, state_idx_rescaled,
         age_group, gender, robot_experience,
         noise_level, noise_level_f, has_noise, suggestion_type,
         has_dx, has_ax, has_ax_only, has_dx_only, has_dxax,
         scenario_completed, num_actions, optimal_dx)

optimal_dx.model.t = loadModel("optimal_dx.model.t")
optimal_dx.model.v = loadModel("optimal_dx.model.v")
```

```{r, fig.width=3.5, fig.height=5}
gg_df =
  plot_df %>%
    mutate(optimal_dx = factor(optimal_dx)) %>%
    mutate(user_id = factor(user_id)) %>%
    mutate(optimal_dx = fct_recode(optimal_dx, incorrect="0", correct = "1"),
           noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0"),
           suggestion_type = fct_recode(suggestion_type, BASELINE="NONE")) %>%
    count(user_id, suggestion_type, noise_level, optimal_dx, num_actions,
          name = "num_optimal_dx")

gg_df %>%
  filter(optimal_dx == "correct") %>%
  ggplot(aes(suggestion_type, num_optimal_dx / num_actions, fill=suggestion_type)) +
    geom_boxplot() +
    facet_grid(rows = vars(noise_level)) +
    labs(y = "Fraction of optimal actions", x = NULL) +
    scale_y_continuous(breaks = c(0, 0.5, 1.0)) +
    scale_fill_economist() +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

Significance Results:

1. Small positive effect of DX
1. Medium positive effect of DXAX
1. Small linear effect of Noise

So the related plots:

```{r, fig.width=3.5, fig.height=2.5}
eff = fixef(optimal_dx.model.t)
base_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  - eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
ax_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
dx_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + (2 * eff["suggestion_type2", "Estimate"])
  - eff["suggestion_type3", "Estimate"]
)
dxax_eff = inv_logit_scaled(
  eff["Intercept", "Estimate"]
  + (3 * eff["suggestion_type3", "Estimate"])
)

gg_df = plot_df %>%
  mutate(scenario_completed = factor(scenario_completed)) %>%
  mutate(scenario_completed = fct_recode(scenario_completed, Unresolved="0", Resolved = "1"),
         has_ax_only = fct_recode(has_ax_only, "No AX"="FALSE", "AX"="TRUE"),
         has_dx_only = fct_recode(has_dx_only, "No DX"="FALSE", "DX"="TRUE"),
         has_dxax = fct_recode(has_dxax, "No DXAX"="FALSE", "DXAX"="TRUE"),
         noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
  count(user_id, suggestion_type, optimal_dx, num_actions, has_ax_only, has_dx_only, has_dxax, noise_level,
        name = "num_optimal_dx") %>%
  mutate(estimate = ifelse(suggestion_type == "NONE", base_eff, -1)) %>%
  mutate(estimate = ifelse(suggestion_type == "AX", ax_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DX", dx_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DXAX", dxax_eff, estimate)) %>%
  mutate(suggestion_type = fct_recode(suggestion_type, BASELINE="NONE"))

gg_df %>%
  filter(optimal_dx == "1") %>%
  ggplot(aes(suggestion_type, num_optimal_dx / num_actions, group = suggestion_type, colour=suggestion_type)) +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    geom_signif(y_position = 1.15, xmin = 1, xmax = 3, annotation = "*", textsize = 8, color = "black") +
    geom_signif(y_position = 1.35, xmin = 1, xmax = 4, annotation = "**", textsize = 8, color = "black") +
    scale_y_continuous(limits = c(0.0, 1.5), breaks = c(0.0, 0.5, 1.0)) +
    labs(y = NULL, x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

```{r, fig.width=3.5, fig.height=2.5}
eff = fixef(optimal_dx.model.v)
noise_0_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f1","Estimate"])
noise_1_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f2","Estimate"])
noise_2_eff = inv_logit_scaled(eff["Intercept", "Estimate"] - eff["noise_level_f1","Estimate"] - eff["noise_level_f2","Estimate"])

gg_df = gg_df %>%
  mutate(estimate = if_else(noise_level == "Acc: 100%", noise_0_eff, estimate)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 90%", noise_1_eff, estimate)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 80%", noise_2_eff, estimate)) %>%
  mutate(noise_level = fct_rev(noise_level))

gg_df %>%
  filter(optimal_dx == "1") %>%
  ggplot(aes(noise_level, num_optimal_dx / num_actions, group = noise_level, colour = noise_level)) +
    geom_hline(yintercept = inv_logit_scaled(eff["Intercept", "Estimate"]),
               size = .7, linetype = "dashed", color = "grey") +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    annotate("segment",
             x = 3, y = noise_0_eff,
             xend = 2, yend = noise_1_eff,
             colour = "black") +
    annotate("segment",
             x = 1, y = noise_2_eff,
             xend = 2, yend = noise_1_eff,
             color = "black") +
    annotate("text",
             x = 3.5,
             y = inv_logit_scaled(eff["Intercept", "Estimate"] - 0.35),
             label = "Mean of all levels",
             angle = 90,
             group = NA,
             colour = "black") +
    scale_y_continuous(limits = c(0.0, 1.0), breaks = c(0.0, 0.5, 1.0)) +
    labs(y = "RDX", x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    scale_size_area(max_size = 1) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
    legend_none()
```

```{r, echo=F, results=F, message=F, warning=F}
rm(optimal_dx.model.t, optimal_dx.model.v)
gc()
```


# Following Action Suggestions

Load the data and the models:

```{r}
plot_df = actions %>%
  filter(has_ax == T) %>%
  select(X1, id, user_id, study_condition, start_condition, num_optimal,
         state_idx, state_idx_rescaled,
         age_group, gender, robot_experience,
         noise_level, noise_level_f, has_noise, suggestion_type,
         has_dx, has_ax, has_ax_only, has_dx_only, has_dxax,
         scenario_completed, num_actions, chose_ax)

chose_ax.model.t = loadModel("chose_ax.model.t")
chose_ax.model.v = loadModel("chose_ax.model.v")
```

```{r, fig.width=3.5, fig.height=5}
gg_df =
  plot_df %>%
    mutate(chose_ax = factor(chose_ax)) %>%
    mutate(user_id = factor(user_id)) %>%
    mutate(chose_ax = fct_recode(chose_ax, no_follow="0", follow = "1"),
           noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
    count(user_id, suggestion_type, chose_ax, num_actions, noise_level,
          name = "num_follow_ax")

gg_df %>%
  filter(chose_ax == "follow") %>%
  ggplot(aes(suggestion_type, num_follow_ax / num_actions, fill=suggestion_type)) +
    geom_boxplot() +
    facet_grid(rows = vars(noise_level)) +
    labs(y = "Fraction of optimal actions", x = NULL) +
    scale_y_continuous(breaks = c(0, 0.5, 1.0)) +
    scale_fill_economist() +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

Significance Results:

No significant results.

Still plotting a linear effect:

```{r, fig.width=3.5, fig.height=5}
eff = fixef(chose_ax.model.v)
noise_0_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f1","Estimate"])
noise_1_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f2","Estimate"])
noise_2_eff = inv_logit_scaled(eff["Intercept", "Estimate"] - eff["noise_level_f1","Estimate"] - eff["noise_level_f2","Estimate"])

gg_df = plot_df %>%
  mutate(chose_ax = factor(chose_ax)) %>%
  mutate(chose_ax = fct_recode(chose_ax, no_follow="0", follow="1"),
         has_dx = fct_recode(has_dx, "No DX"="FALSE", "DX"="TRUE"),
         noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
  count(user_id, suggestion_type, chose_ax, num_actions, has_dx, noise_level,
        name = "num_follow_ax") %>%
  mutate(estimate = if_else(noise_level == "Acc: 100%", noise_0_eff, -1)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 90%", noise_1_eff, estimate)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 80%", noise_2_eff, estimate)) %>%
  mutate(noise_level = fct_rev(noise_level))

gg_df %>%
  filter(chose_ax == "follow") %>%
  ggplot(aes(noise_level, num_follow_ax / num_actions, group = noise_level, colour = noise_level)) +
    geom_hline(yintercept = inv_logit_scaled(eff["Intercept", "Estimate"]),
               size = .7, linetype = "dashed", color = "grey") +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    annotate("segment",
             x = 3, y = noise_0_eff,
             xend = 2, yend = noise_1_eff,
             colour = "black") +
    annotate("segment",
             x = 1, y = noise_2_eff,
             xend = 2, yend = noise_1_eff,
             color = "black") +
    annotate("text",
             x = 3.5,
             y = inv_logit_scaled(eff["Intercept", "Estimate"] - 0.35),
             label = "Mean of all levels",
             angle = 90,
             group = NA,
             colour = "black") +
    scale_y_continuous(limits = c(0.0, 1.0), breaks = c(0.0, 0.5, 1.0)) +
    labs(y = "RDX", x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    scale_size_area(max_size = 1) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
    legend_none()
```

```{r, echo=F, results=F, message=F, warning=F}
rm(chose_ax.model.t, chose_ax.model.v)
gc()
```


# Following Diagnosis Suggestions

Load the data and the models:

```{r}
plot_df = actions %>%
  filter(has_dx == T) %>%
  select(X1, id, user_id, study_condition, start_condition, num_optimal,
         state_idx, state_idx_rescaled,
         age_group, gender, robot_experience,
         noise_level, noise_level_f, has_noise, suggestion_type,
         has_dx, has_ax, has_ax_only, has_dx_only, has_dxax,
         scenario_completed, num_actions, chose_dx)

chose_dx.model.t = loadModel("chose_dx.model.t")
chose_dx.model.v = loadModel("chose_dx.model.v")
```

```{r, fig.width=3.5, fig.height=5}
gg_df =
  plot_df %>%
    mutate(chose_dx = factor(chose_dx)) %>%
    mutate(user_id = factor(user_id)) %>%
    mutate(chose_dx = fct_recode(chose_dx, no_follow="0", follow = "1"),
           noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
    count(user_id, suggestion_type, chose_dx, num_actions, noise_level,
          name = "num_follow_dx")

gg_df %>%
  filter(chose_dx == "follow") %>%
  ggplot(aes(suggestion_type, num_follow_dx / num_actions, fill=suggestion_type)) +
    geom_boxplot() +
    facet_grid(rows = vars(noise_level)) +
    labs(y = "Fraction of optimal actions", x = NULL) +
    scale_y_continuous(breaks = c(0, 0.5, 1.0)) +
    scale_fill_economist() +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

Significance Results:

1. Small linear effect of noise

So the related plots:

```{r, fig.width=3.5, fig.height=5}
eff = fixef(chose_dx.model.v)
noise_0_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f1","Estimate"])
noise_1_eff = inv_logit_scaled(eff["Intercept", "Estimate"] + eff["noise_level_f2","Estimate"])
noise_2_eff = inv_logit_scaled(eff["Intercept", "Estimate"] - eff["noise_level_f1","Estimate"] - eff["noise_level_f2","Estimate"])

gg_df = plot_df %>%
  mutate(chose_dx = factor(chose_dx)) %>%
  mutate(chose_dx = fct_recode(chose_dx, no_follow="0", follow="1"),
         has_ax = fct_recode(has_ax, "No AX"="FALSE", "AX"="TRUE"),
         noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
  count(user_id, suggestion_type, chose_dx, num_actions, has_ax, noise_level,
        name = "num_follow_dx") %>%
  mutate(estimate = if_else(noise_level == "Acc: 100%", noise_0_eff, -1)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 90%", noise_1_eff, estimate)) %>%
  mutate(estimate = if_else(noise_level == "Acc: 80%", noise_2_eff, estimate)) %>%
  mutate(noise_level = fct_rev(noise_level))

gg_df %>%
  filter(chose_dx == "follow") %>%
  ggplot(aes(noise_level, num_follow_dx / num_actions, group = noise_level, colour = noise_level)) +
    geom_hline(yintercept = inv_logit_scaled(eff["Intercept", "Estimate"]),
               size = .7, linetype = "dashed", color = "grey") +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    annotate("segment",
             x = 3, y = noise_0_eff,
             xend = 2, yend = noise_1_eff,
             colour = "black") +
    annotate("segment",
             x = 1, y = noise_2_eff,
             xend = 2, yend = noise_1_eff,
             color = "black") +
    annotate("text",
             x = 3.5,
             y = inv_logit_scaled(eff["Intercept", "Estimate"] - 0.35),
             label = "Mean of all levels",
             angle = 90,
             group = NA,
             colour = "black") +
    scale_y_continuous(limits = c(0.0, 1.0), breaks = c(0.0, 0.5, 1.0)) +
    labs(y = "RDX", x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    scale_size_area(max_size = 1) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
    legend_none()
```

```{r, echo=F, results=F, message=F, warning=F}
rm(chose_dx.model.t, chose_dx.model.v)
gc()
```


# SUS

Load the data and the models:

```{r}
plot_df = users %>%
  select(X1, id, study_condition, start_condition, num_optimal,
         age_group, gender, robot_experience,
         noise_level, noise_level_f, has_noise, suggestion_type,
         has_dx, has_ax, has_ax_only, has_dx_only, has_dxax,
         sus, scenario_completed) %>%
  mutate(scenario_completed = factor(scenario_completed))

sus.model.t = loadModel("sus.model.t")
sus.model.v = loadModel("sus.model.v")
```

```{r, fig.width=3.5, fig.height=5}
gg_df = plot_df %>%
  mutate(noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0"),
         suggestion_type = fct_recode(suggestion_type, BASELINE="NONE")) %>%
  group_by(suggestion_type, noise_level) %>%
  summarise(mad = mad(sus), sus = median(sus))

gg_df %>%
  ggplot(aes(suggestion_type, sus, fill=suggestion_type)) +
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = sus-mad, ymax = sus+mad), width = 0) +
    facet_grid(rows = vars(noise_level)) +
    labs(y = "SUS Score", x = NULL) +
    scale_y_continuous(breaks = c(0, 50, 100), limits = c(0, 100)) +
    scale_fill_economist() +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

Significance Results:

1. Insignificant effect of AX
1. Insignificant effect of DX

So the related plots:

```{r, fig.width=3.5, fig.height=5}
eff = fixef(sus.model.t)
base_eff = (
  eff["Intercept", "Estimate"]
  - eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
ax_eff = (
  eff["Intercept", "Estimate"]
  + eff["suggestion_type1", "Estimate"]
  - eff["suggestion_type2", "Estimate"]
  - eff["suggestion_type3", "Estimate"]
)
dx_eff = (
  eff["Intercept", "Estimate"]
  + (2 * eff["suggestion_type2", "Estimate"])
  - eff["suggestion_type3", "Estimate"]
)
dxax_eff = (
  eff["Intercept", "Estimate"]
  + (3 * eff["suggestion_type3", "Estimate"])
)

gg_df = plot_df %>%
  mutate(has_ax_only = fct_recode(has_ax_only, "No AX"="FALSE", "AX"="TRUE"),
         has_dx_only = fct_recode(has_dx_only, "No DX"="FALSE", "DX"="TRUE"),
         has_dxax = fct_recode(has_dxax, "No DXAX"="FALSE", "DXAX"="TRUE"),
         noise_level = fct_recode(noise_level, "Acc: 100%"="0.0", "Acc: 90%"="1.0", "Acc: 80%"="2.0")) %>%
  mutate(estimate = ifelse(suggestion_type == "NONE", base_eff, -1)) %>%
  mutate(estimate = ifelse(suggestion_type == "AX", ax_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DX", dx_eff, estimate)) %>%
  mutate(estimate = ifelse(suggestion_type == "DXAX", dxax_eff, estimate)) %>%
  mutate(suggestion_type = fct_recode(suggestion_type, BASELINE="NONE"))

gg_df %>%
  ggplot(aes(suggestion_type, sus, group = suggestion_type, colour=suggestion_type)) +
    geom_count(aes(colour = NULL)) +
    geom_boxplot(aes(y = estimate)) +
    # scale_y_continuous(limits = c(0.0, 1.2), breaks = c(0.0, 0.5, 1.0)) +
    labs(y = NULL, x = NULL) +
    scale_colour_manual(values = c("#e51400", "#008a00", "#f0a30a", "#a4c400")) +
    theme_economist_white(base_size = 13) +
    theme(plot.background = element_rect(fill = "white"),
          axis.title.y = element_blank()) +
    legend_none()
```

```{r, echo=F, results=F, message=F, warning=F}
rm(sus.model.t, sus.model.v)
gc()
```
